\section{Advanced parameters}
\label{sec:advanced}

The bottom collapsible section on the left sidebar holds parameters
that most users leave at their defaults. Expand it only if you are
debugging convergence or doing cutting-edge experiments.

\subsection{Initial Guess}

Controls how IC-GN gets its starting displacement for each frame.
Four mutually-exclusive options:

\begin{description}[leftmargin=1.2cm,style=nextline]
  \item[Previous frame (default, fastest)]
    Warm-start from the previous frame's converged result. Best for
    smooth, slow motion. Automatically selected when Tracking Mode is
    Accumulative.
  \item[FFT when reference frame updates]
    Run an FFT cross-correlation whenever a new reference frame is
    adopted; warm-start within each segment. This is the default for
    Incremental mode.
  \item[FFT every frame (safest)]
    Full FFT every frame. Eliminates warm-start error propagation
    across frames, but slowest. Use for unpredictable motion
    (oscillation, impact, random).
  \item[Reset FFT every N frames]
    Full FFT every $N$ frames, warm-start in between. Bounds the
    worst-case warm-start error to $N$ frames.
\end{description}

\subsection{Auto-expand search on clipped peaks}

Checkbox, on by default. When the FFT NCC peak lands on the edge of
the search window (indicating the true displacement is larger), the
pipeline automatically retries with $2\times$ search range up to six
times, capped at $\min(H, W) / 2$. Leave this on unless you are
debugging FFT behaviour.

\subsection{Mesh appearance}

Cosmetic only. Choose the colour and line width of the mesh overlay
drawn on the canvas (does not affect computation).
