\section{Running the DIC}
\label{sec:running}

\subsection{The Run button}

The big blue \textbf{Run DIC Analysis} button at the top of the
right sidebar starts the pipeline. It is disabled until:
\begin{itemize}
  \item At least 2 images are loaded,
  \item Frame 1 has a non-empty Region of Interest.
\end{itemize}

If either condition fails, clicking Run (or trying to) raises a
modal dialog telling you exactly what is missing.

\subsection{Cancelling}

Below Run is a single red \textbf{Cancel} button (replaces the older
Pause + Stop pair). It is enabled while the pipeline is running.

Cancelling stops the current run cleanly: already-computed frames
are kept, no further frames are processed, and state returns to
IDLE (not DONE, so the Export button stays disabled).

\subsection{Progress display}

Below the Cancel button:

\begin{itemize}
  \item Thin blue progress bar (0--100 \% of the full pipeline).
  \item Text label with the current stage
        (\emph{Section 3: FFT initial search},
        \emph{Section 6: IC-GN local solve},
        \emph{S8: Frame 5/19}, \ldots).
  \item ELAPSED / REMAINING timestamps.
\end{itemize}

\subsection{Fatal errors}

The console log (bottom of the right sidebar) collects every info,
warning, and error message with a timestamp. \emph{Fatal} errors
(missing images, Region of Interest too small, pipeline-side
exceptions) also trigger a modal dialog. The dialog shows a plain-
English summary; the full traceback stays in the console log.

\begin{warnbox}
The console can scroll off-screen if many info messages accumulate.
Fatal errors will not be missed because of the modal dialog, but
warnings can be. If something looks wrong, check the console log.
\end{warnbox}

\subsection{Completion}

When the run finishes cleanly, the Strain Post-Processing window
opens automatically (see section \ref{sec:strain-processing}). The
Run button re-enables for another run; the Export button becomes
active.

If the run is cancelled or fails, Strain does not open automatically
and Export stays disabled.
