\section{Viewing results}
\label{sec:viewing-results}

After a run, the right sidebar populates with field-viewing
controls. The canvas shows a colour-mapped overlay of the selected
field on the background image.

\subsection{FIELD section}

Two toggle buttons (exclusive): \textbf{Disp U} and \textbf{Disp V}.
Selected field is highlighted; clicking the other switches.

Below the toggles, the \emph{Show on deformed frame} checkbox (see
Section~\ref{sec:canvas}) controls whether the overlay plots on the
deformed frame or the reference.

\subsection{VISUALIZATION section}

\subsubsection*{Colormap}

Eight built-in maps: \texttt{jet}, \texttt{viridis}, \texttt{turbo},
\texttt{coolwarm}, \texttt{plasma}, \texttt{inferno},
\texttt{RdBu\_r}, \texttt{seismic}.

\emph{RdBu\_r} and \emph{seismic} are diverging (white at zero);
best for displacement that crosses zero.

pyALDIC remembers the colormap choice per-field. Switching from
\texttt{disp\_u} to \texttt{disp\_v} restores whatever map you set
last time for that field.

\subsubsection*{Color Range}

\begin{description}[leftmargin=1.2cm,style=nextline]
  \item[Auto (default)]
    Range is set from the 2--98 percentile of visible node values
    (excludes extreme outliers but uses real data).
  \item[Manual]
    Uncheck Auto, then type \emph{Min} and \emph{Max} explicitly.
    Useful for reporting (all frames share one range) or when you
    know the physically meaningful bounds.
\end{description}

\subsubsection*{Opacity}

Slider (0--100\%). Default 70\%. Adjusts the alpha blending between
the field overlay and the background image.

\subsection{PHYSICAL UNITS section}

A checkbox plus two fields:

\begin{description}[leftmargin=1.2cm,style=nextline]
  \item[Pixel Size]
    Numeric value, dropdown unit (nm, \textmu m, mm, cm, m, inch).
    Converts raw pixel displacements to physical length on all
    displacement-family fields.
  \item[Frame Rate]
    Used to convert inter-frame velocity ($\Delta U / $ frame) to
    physical speed (length / s).
\end{description}

Strain fields are dimensionless and unaffected by these settings.

\subsection{Console log}

Scrollable read-only widget at the bottom of the right sidebar.
Colour-coded by severity:

\begin{center}
\begin{tabular}{ll}
  \toprule
  Level & Colour \\
  \midrule
  info     & blue / white \\
  warning  & yellow       \\
  error    & red          \\
  success  & green        \\
  \bottomrule
\end{tabular}
\end{center}

Every line is prefixed with a \texttt{HH:MM:SS} timestamp.
